A hierarchical approach for modelling X-ray beamlines. Application to a coherent beamline.

### 2019-06-21 paper-hierarchical.tex
last fixes

One can also make some simple inferences about the beam coherence. The coherent fraction (CF) \cite{arxivCF} of the undulator beam is the occupation of the lowest coherent mode and will be discussed further in Section~\ref{level2}. An approximated estimation of CF can be obtained using Eqs.~\ref{eq:photon small sigmas} and \ref{eq:photon big sigmas}. The coherent fraction is the ratio of the phase space of the fully coherent (zero emittance) beam relative to the true beam. The CF in the horizontal and vertical planes are
\begin{equation}\label{eq:coherent fraction}
 CF_{(h,v)} = \frac{\sigma_u \sigma'_u}{\Sigma_{(h,v)} \Sigma'_{(h,v)}},
\end{equation}
and the total coherent fraction is the product of both (CF=CF$_h \times $CF$_v$). An estimation of the CF calculated in this way gives CF=0.12\% for the ESRF-1 and 2.73\% for EBS at 17 keV photon energy. The CF roughly indicates the ratio of the ``coherent photons'' over the total number of photons. It is a good indicator of the quality of a coherent beam (a fully coherent beam has CF=1 and an incoherent beam CF=0). The beamline optics act as a ``coherence filter'' by removing the ``bad'' or ``incoherent'' photons and in consequence increasing the CF. A complete cleaning is impossible because of the spatial overlapping of the different coherence modes. However, apertures centered at the optical axis would clean the beam from these undesired photons. If we compare the values of the beamline transmission due to the geometrical aperture  (0.2\% for ESRF-1 and 2.95\% for EBS) with the CF values, we remark that they are very close. This suggests that the beam at the focal position will be highly coherent because the fraction of the photons removed from the beam matches the CF value that quantifies the fraction of ``good'' or ``coherent'' photons.

@@

\begin{figure}\label{fig:metrology}
\includegraphics[width=0.9\textwidth]{GRAPHICS/metrology.eps}
\caption{Error height profiles used for the simulations (left) and power spectral density (right) for the ML monochromator (top row), the KB vertical focusing mirror (central row), and the KB horizontal focusing mirror (bottom row).}
\end{figure}

>>>>

One can also make some simple inferences about the beam coherence. The coherent fraction (CF) \cite{arxivCF} of the undulator beam is the occupation of the lowest coherent mode and will be discussed further in Section~\ref{level2}. An approximated estimation of CF can be obtained using Eqs.~\ref{eq:photon small sigmas} and \ref{eq:photon big sigmas}. The coherent fraction is the ratio of the phase space of the fully coherent (zero emittance) beam relative to the true beam. The CF in the horizontal and vertical planes are
\begin{equation}\label{eq:coherent fraction}
 CF_{(h,v)} = \frac{\sigma_u \sigma'_u}{\Sigma_{(h,v)} \Sigma'_{(h,v)}},
\end{equation}
and the total coherent fraction is the product of both (CF=CF$_h \times $CF$_v$). An estimation of the CF calculated in this way gives CF=0.12\% for the ESRF-1 and 2.73\% for EBS at 17 keV photon energy. The CF roughly indicates the ratio of the ``coherent photons'' over the total number of photons. It is a good indicator of the quality of a coherent beam (a fully coherent beam has CF=1 and an incoherent beam CF=0). The beamline optics act as a ``coherence filter'' by removing the ``bad'' or ``incoherent'' photons and in consequence increasing the CF. A complete cleaning is impossible because of the spatial overlapping of the different coherence modes. However, apertures centered at the optical axis would clean the beam from these undesired photons. If we compare the values of the beamline transmission due to the geometrical aperture  (0.21\% for ESRF-1 and 2.85\% for EBS) with the CF values, we remark that they are very close. This suggests that the beam at the focal position will be highly coherent because the fraction of the photons removed from the beam matches the CF value that quantifies the fraction of ``good'' or ``coherent'' photons.

@@

\begin{figure}\label{fig:metrology}
\includegraphics[width=0.9\textwidth]{GRAPHICS/metrology.pdf}
\caption{Error height profiles used for the simulations (left) and power spectral density (right) for the ML monochromator (top row), the KB vertical focusing mirror (central row), and the KB horizontal focusing mirror (bottom row).}
\end{figure}
